Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns

### 2018-03-03 manuscript.Rnw
Add Pagel's correlated evo test to manuscript
Also, change font to TNR in MS and SI

% run this from the command line to compile: Rscript -e "library(knitr); knit('./manuscript.Rnw')"
\documentclass{article}

@@

@@

@@

<<run_analyses, results="hide">>=
# set working directory, run all analyses, save results objects
setwd(here::here())
source(file = "bin/microclimate.R")
source(file = "bin/trait_PCA.R")
source(file = "bin/cont_phylosig.R")
source(file = "bin/binary_phylosig.R")
source(file = "bin/sporo_PIC.R")
source(file = "bin/binaryPGLMM.R")
save(list = ls(all = TRUE), file= "results.RData")
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Summary %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

@@

print(xtable(PIC.results,
             label="table:PIC_sporo",
             caption="Results of phylogenetically independent contrasts analysis of quantitative (sporophyte) traits related to epiphytic growth. All trait contrasts were made by subtracting epiphytic values from terrestrial values; thus, a positive contrast indicates greater values for terrestrial clades. Significant differences between epiphytes and terrestrial clades in bold."),
      sanitize.colnames.function = custom_cols,
      sanitize.rownames.function = custom_rows,
      sanitize.text.function = function (x) {x},
      include.rownames=TRUE,
      caption.placement="top")
@
%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage

>>>>

\documentclass{article}

@@

% Use Times New Roman font (better conversion of special characters in Word)
\usepackage{fontspec}
\setmainfont{Times New Roman}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title Page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

<<run_analyses, results="hide">>=
# set working directory, run all analyses, save results objects
setwd(here::here())
source(file = "bin/microclimate.R")
source(file = "bin/trait_PCA.R")
source(file = "bin/cont_phylosig.R")
source(file = "bin/binary_phylosig.R")
source(file = "bin/sporo_PIC.R")
source(file = "bin/correlated_evo.R")
source(file = "bin/binaryPGLMM.R")
save(list = ls(all = TRUE), file= "results.RData")
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Summary %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage

@@

print(xtable(PIC.results,
             label="table:PIC_sporo",
             caption="Results of phylogenetically independent contrasts analysis of quantitative (sporophyte) traits related to epiphytic growth. All trait contrasts were made by subtracting epiphytic values from terrestrial values; thus, a positive contrast indicates greater values for terrestrial clades. Significant differences between epiphytes and terrestrial clades in bold."),
      sanitize.colnames.function = custom_cols,
      sanitize.rownames.function = custom_rows,
      sanitize.text.function = function (x) {x},
      include.rownames=TRUE,
      caption.placement="top")
@

% Table 4
\clearpage

<<pagel_test, results="asis">>=
pagel.results <- round_df(pagel.results)
pagel.results <- embolden_p(pagel.results, col.select=c("pval"))

print(xtable(pagel.results,
             label="table:pagel_gameto",
             caption="Pagel's \\citeyearpar{Pagel1994} test of correlated evolution between binary traits. Each gametophyte trait was coded as a binary trait and tested for correlated evolution with growth habit (epiphytic vs. terrestrial). Models with significantly different log likelihoods (LL) in bold; lower LL for the dependent model indicates correlation with growth habit."),
      sanitize.colnames.function = custom_cols,
      sanitize.rownames.function = custom_rows,
      sanitize.text.function = function (x) {x},
      include.rownames=TRUE,
      caption.placement="top")
@

%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
